%! TeX program = lualatex
\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{kotex}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{fontspec}
\usepackage[sc,osf]{mathpazo}
\usepackage[ttscale=0.8]{libertine}

\def\myname{Chiwan Park}
\def\myphone{+82-10-8518-3832}
\def\myaddress{Advanced Recommendation Technologies Team, Kakao Corp.\\
7F, Building N, H-Square,\\
235 Pangyoyeok-ro, Bundang-gu, Seongnam-si, Gyeonggi-do,\\
Republic of Korea 13494}
\def\myemail{chiwanpark@hotmail.com}
\def\myhomepage{https://chiwanpark.com}

\hypersetup{%
  pdftitle={Curriculum Vitae},
  pdfauthor={\myname},
  pdfsubject={},
  pdfkeywords={\myname, Curriculum Vitae},
  plainpages=false,
  bookmarksnumbered=true,
  pdfstartview={FitV},
  colorlinks={false},
  pdfborder={0 0 0},
  pdfcreator={LuaTeX}
}

\pagestyle{myheadings}
\markright{\myname}
\thispagestyle{empty}

\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

\setlength{\parskip}{-0.4em}
\setlength\parindent{0em}
\titlespacing{\section}{0pt}{\parskip}{-\parskip}

\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.5em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\begin{document}

% HEADER
\par{\Huge \textsc{\myname}}

\bigskip

\begin{minipage}[t]{0.625\textwidth}
  \myaddress
\end{minipage}
\begin{minipage}[t]{0.375\textwidth}
  Phone: \myphone\\
  E-Mail: \href{mailto:\myemail}{\texttt{\myemail}}\\
  Homepage: \href{\myhomepage}{\texttt{\myhomepage}}
\end{minipage}

% RESEARCH INTERESTS
\section*{Research Interests}
\begin{itemize}
  \item \textbf{Recommender Systems:} designing and developing machine learning models for recommender systems based on user activities, contents information, and social graphs.
  \item \textbf{Large-scale Graph Processing:} designing algorithms for analyzing and discovering useful information from real-world graphs by exploiting properties of the graphs.
\end{itemize}

% EDUCATION
\section*{Education}
\begin{itemize}
  \item \textbf{Master of Science}, Computer Science and Engineering\hfill\textsc{Mar. 2016 -- Feb. 2018}\\
        Seoul National University\\
        Advisor: U Kang
  \item \textbf{Bachelor of Science}, Earth System Sciences\hfill\textsc{Mar. 2010 -- Feb. 2016}\\
        \textbf{Bachelor of Engineering}, Computer Science (Double Major)\\
        Yonsei University
\end{itemize}

% PUBLICATIONS
\section*{Publications}
\begin{itemize}
  \item Simple and Efficient Recommendation Strategy for Warm/Cold Sessions for RecSys Challenge 2022\\
  Hyunsung Lee, Sungwook Yoo, Andrew Yang, Wonjun Jang and \textbf{Chiwan Park}\\
  RecSys Challenge Workshop at the 16th ACM Conference on Recommender Systems (RecSys), 2022
  \item FlexGraph: Flexible partitioning and storage for scalable graph mining\\
  \textbf{Chiwan Park}, Ha-Myung Park and U Kang\\
  PLoS ONE 15(1): e0227032
  \item PegasusN: A Scalable and Versatile Graph Mining System\\
  Ha-Myung Park, \textbf{Chiwan Park}, and U Kang\\
  Thirty-Second AAAI Conference on Artificial Intelligence (AAAI) 2018 (Demo Paper)
  \item A Distributed Vertex Rearrangement Algorithm for Compressing and Mining Big Graphs\\
  Namyong Park, \textbf{Chiwan Park}, and U Kang\\
  Journal of KIISE, Vol. 43, No. 10, pp. 1131-1143, 2016.
\end{itemize}

% PATENTS
\section*{Patents}
\begin{itemize}
  \item U Kang, \textbf{Chiwan Park}, Ha-Myung Park, Minji Yoon, "Method and Apparatus for Scalable Graph Mining using Graph Pre-partitioning", Korean patent number: 10-1990735 (filed on Mar. 30, 2018, and registered on Jun. 12, 2019).
\end{itemize}

% HONORS AND AWARDS
\section*{Honors and Awards}
\subsection*{Scholarship}
\begin{itemize}
	\setlength\itemsep{0.1em}
  \item \textbf{Honor Scholarship}, Yonsei University\hfill\textsc{Feb. 2015}
  \item \textbf{Sinchon Market Supporters Scholarship} (merit-based), Yonsei University\hfill\textsc{Nov. 2014}
  \item \textbf{Geoscience Scholarship}, Ministry of Knowledge and Economy\hfill\textsc{Sep. 2012}
\end{itemize}
\subsection*{Fellowship}
\begin{itemize}
  \item \textbf{Global Open Frontier Program}\hfill\textsc{Dec. 2013 -- Dec. 2015}\\
        National IT Industry Promotion Agency of Korea
  \item \textbf{Support for Open Source Software Development}\hfill\textsc{Jul. 2013 -- Nov. 2013}\\
        National IT Industry Promotion Agency of Korea
\end{itemize}
\subsection*{Awards}
\begin{itemize}
  \item \textbf{Special Contribution Award} of 10th CJK OSS Award\hfill\textsc{Nov. 2015}\\
        Northeast Asia OSS Promotion Forum
  \item \textbf{3rd Prize} of Korea Big Data Analysis Contest 2013\hfill\textsc{Nov. 2013}\\
        National Information Society Agency of Korea
  \item \textbf{3rd Prize} of SK Telecom Mobile Web Application Contest 2013\hfill\textsc{Dec. 2013}\\
        SK Telecom
  \item \textbf{Participation Award} of 26th Korea Olympiad in Informatics\hfill\textsc{Jul. 2009}\\
        Ministry of the Interior and Safety
\end{itemize}

% TEACHING EXPERIENCES
\section*{Teaching Experiences}
\begin{itemize}
	\setlength\itemsep{0.1em}
	\item \textbf{Teaching Assistant}, Basic Math for Big Data at SNU BDI Academy\hfill\textsc{Summer 2017}
	\item \textbf{Teaching Assistant}, M1522.001400 Introduction to Data Mining at SNU\hfill\textsc{Spring 2017}
	\item \textbf{Teaching Assistant}, M1522.000900 Data Structures at SNU\hfill\textsc{Fall 2016}
\end{itemize}

% WORK EXPERIENCES
\section*{Work Experiences}
\begin{itemize}
	\setlength\itemsep{0.1em}
  \item \textbf{Research Engineer (Full-time)} at Kakao\hfill\textsc{Apr. 2018 -- Present}
  \item \textbf{Software Engineer (Part-time)} at Anbado Video\hfill\textsc{Jan. 2014 -- Apr. 2015}
  \item \textbf{Software Engineer (Part-time)} at Cloudine\hfill\textsc{Jul. 2013 -- Dec. 2013}
\end{itemize}

% GRADUATE COURSEWORK
\section*{Graduate Coursework}
\begin{itemize}
	\setlength\itemsep{0.1em}
  \item M1522.001600 (002), Advanced Deep Learning at SNU\hfill\textsc{Fall 2017}
	\item M1522.001600 (001), Large Scale Data Analysis using Deep Learning at SNU\hfill\textsc{Spring 2017}
	\item M1522.001600 (002), Advanced Social Network Analysis at SNU\hfill\textsc{Spring 2017}
	\item 430.555, Knowledge and Database Management Systems at SNU\hfill\textsc{Fall 2016}
	\item M1522.001300, Probabilistic Graphical Models at SNU\hfill\textsc{Fall 2016}
	\item 4190.671, System Performance Evaluation at SNU\hfill\textsc{Spring 2016}
	\item 4190.684, Distributed Systems at SNU\hfill\textsc{Spring 2016}
\end{itemize}

% EXTRA ACTIVITIES
\section*{Extra Activities}
\begin{itemize}
	\setlength\itemsep{0.1em}
  \item \textbf{System Administrator} of SNU Data Mining Lab.\hfill\textsc{Mar. 2016 -- Mar. 2018}
  \item \textbf{Homepage Administrator} of SNU Data Mining Lab.\hfill\textsc{Mar. 2016 -- Mar. 2018}
  \item \textbf{Committer} of Apache Flink\hfill\textsc{Nov. 2014 -- Present}
  \item \textbf{Trainee} of 3rd Software Maestro Program\hfill\textsc{Jul. 2012 -- Jun. 2013}
\end{itemize}

% TALKS
\section*{Talks}
\begin{itemize}
  \item \href{https://speakerdeck.com/chiwanpark/challenges-in-real-world-recommender-systems}{\textit{Challenges in Real-world Recommender Systems}}\hfill\textsc{Jun. 2022}\\
        KCC 2022, Jeju, Korea
  \item \href{http://j.mp/chiwanpark-ifkakao2019}{\textit{상품 카탈로그 자동 생성 ML 모델 소개}}\hfill\textsc{Aug. 2019}\\
        if kakao(dev) 2019, Seoul, Korea
  \item \href{http://j.mp/d2-campus-seminar-4th-park}{\textit{학교에선 알려주지 않는 오픈 소스 이야기}}\hfill\textsc{Feb. 2016}\\
        NAVER 4th D2 Campus Seminar, Seongnam, Korea
  \item \href{http://j.mp/ossdevconf-2015-park}{\textit{Introduction to Apache Flink}}\hfill\textsc{Dec. 2015}\\
        Open-source Software Developer Center Conference, Seoul, Korea
  \item \href{http://j.mp/cjkossforum-2015-park}{\textit{Lessons Learned from Open-source Activities}}\hfill\textsc{Nov. 2015}\\
        The 14th Northeast Asia OSS Promotion Forum, Tokyo, Japan
\end{itemize}

% REFERENCES
\section*{References}
\begin{itemize}
  \item \textbf{Prof. U Kang}\\
        Department of Computer Science and Engineering\\
        Seoul National University\\
        Seoul, Korea\\
        \href{mailto:ukang@snu.ac.kr}{\texttt{ukang@snu.ac.kr}}
\end{itemize}

\bigskip
{\small Last updated: \today}

\end{document}
